Deciphering the Relationship Betweeen Race, Income, and Political Support in the 2020 United States Election

### 2024-03-15 paper/paper.qmd
second draft of results section

vote_summary <- ces2020 %>%
  group_by(vote) %>%
  summarise(Count = n()) %>%
  mutate(Percentage = Count / sum(Count) * 100)
```

@@

The effect of Race on voting likelihood was positive, indicating that older individuals were more likely to vote than younger ones. The median estimate of the Race coefficient was [insert value], with a 95% credible interval of [insert range], suggesting a significant relationship between age and voting behavior.

(Graphically, this could be represented by a plot showing the probability of voting across different ages, highlighting the increasing trend.)

### Income

Income showed a differential impact on voting likelihood, with higher levels of education associated with an increased probability of voting. The model estimates for each income level, relative to the baseline category, illustrate this pattern clearly.

(A table would summarize the coefficient estimates for income levels, and a graph could show the voting probability by income level, emphasizing the gradient of increasing likelihood with higher income.)

>>>>

vote_summary <- ces2020 %>%
  group_by(CC20_401) %>%
  summarise(Count = n()) %>%
  mutate(Percentage = Count / sum(Count) * 100)
```

@@

The effect of Race on voting likelihood was positive, indicating that older individuals were more likely to vote than younger ones. The median estimate of the Race coefficient was [insert value], with a 95% credible interval of [insert range], suggesting a significant relationship between age and voting behavior. This is further represented in Table ?

```{r}
#| label: tbl-bidenrace
#| tbl-cap: "The Effect of Race on Voting for Biden"
#| echo: false
options(repos = c(CRAN = "https://cloud.r-project.org"))

biden_vote_proportion <- ces2020 %>%
  group_by(race) %>%
  summarise(Proportion_for_Biden = mean(CC20_401 == 1, na.rm = TRUE)) %>%
  ungroup()

ggplot(biden_vote_proportion, aes(x = race, y = Proportion_for_Biden)) +
  geom_col(fill = "blue") +  
  labs(title = "Proportion of Respondents Voting for Biden by Race",
       x = "Race",
       y = "Proportion Voting for Biden") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Income
Income showed a differential impact on voting likelihood, with higher levels of education associated with an increased probability of voting. The model estimates for each income level, relative to the baseline category, illustrate this pattern clearly.

```{r}
#| label: tbl-bidenincome
#| tbl-cap: "The Effect of Income on Voting for Biden"
#| echo: false
options(repos = c(CRAN = "https://cloud.r-project.org"))

income_levels <- data.frame(income = seq(min(ces2020$faminc_new, 
                                             na.rm = TRUE), 
                                        max(ces2020$faminc_new, 
                                            na.rm = TRUE), 
                                        length.out = 100))
# Predict probabilities
income_levels$prob_vote_biden <- predict(model, newdata = income_levels, 
                                         type = "response")

# Plot the probabilities
ggplot(income_levels, aes(x = faminc_new, y = prob_vote_biden)) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = 0, ymax = prob_vote_biden), fill = "blue", alpha = 0.2) +
  labs(title = "Predicted Probability of Voting for Biden by Income Level",
       x = "Income Level",
       y = "Probability of Voting for Biden") +
  theme_minimal()
```
